---
title: "Customer Satisfaction MOPC"
author: "Dennis Murithi"
date: "10/03/2022"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      fig.align = "centre")
```

```{r}
library(tidyverse)
```

```{r}
data<-read.csv("C://Users//adm//Desktop//HCQ//Research dept//MedicalOutpatientCli_DATA_LABELS_2022-03-09_1207.csv")
head(data)
```

# Exploratory Data Analysis.

## How  you would rate the following aspects in the clinic today.

###  Cleaniliness.
```{r fig.cap= "figure 1"}
ggplot(data = data,aes(x=factor(Cleanliness),
                       y=prop.table(stat(count)),
                         fill=factor(Cleanliness),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_viridis_d(begin=0, end = .95,option='D')+
  labs(x="Cleanliness rating",y="Percentage proportion",title = "Categorizationof cleanliness in the hospital")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```

The above plot is very effective in showing how cleanliness was rated by different customers in the hospital.A majority of the customers that is, 37.61% rated it as **very good**, following closely was **excellent** at 31.19 % . **Neutral** came in third at 0.61% and finally those who rated it as fair were 0.31%.There was no customer who rated the hospital cleanliness as poor.

## Customer friendliness.
```{r}
ggplot(data = data,aes(x=factor(Customer.friendliness),
                       y=prop.table(stat(count)),
                         fill=factor(Customer.friendliness),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Dark2")+
  theme_light()+
  labs(x="Customer friendliness rating",y="Percentage proportion",title = " Customer friendliness in the hospital")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```
```{r eval=FALSE}
table(data$Customer.friendliness)
```
Majority of the respondents 34.25% (n=112) termed customer friendliness in the hospital as *very good*,*good* was at 33.94% (n=111). Those who felt customer friendliness was *excellent* accounted for 22.94% (n=75). *Neutral*,*fair* and *poor*came in forth ,fifth and sixth at 4.53%(n=15),2.45% (n=8) and 1.83% (n=6) respectively.

## Security
```{r}
ggplot(data = data,aes(x=factor(Security),
                       y=prop.table(stat(count)),
                         fill=factor(Security),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Accent")+
  theme_light()+
  labs(x="Security rating",y="Percentage proportion",title = " Security in the hospital")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```

## Privacy.
```{r}
ggplot(data = data,aes(x=factor(Privacy),
                       y=prop.table(stat(count)),
                         fill=factor(Privacy),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Paired")+
  theme_update()+
  labs(x="Privacy rating",y="Percentage proportion",title = " Privacy rating in the hospital")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```

## Did the doctor talk to you in a courteous manner? 
```{r}
ggplot(data = data,aes(x=factor(Did.the.doctor.talk.to.you.in.a.courteous.manner.),
                       y=prop.table(stat(count)),
                         fill=factor(Did.the.doctor.talk.to.you.in.a.courteous.manner.),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Accent")+
  theme_light()+
  labs(x="Did the doctor talk to you in a courteous manner?",y="Percentage proportion",title = " ")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```

## During triage were you handled courteously? 
```{r}
ggplot(data = data,aes(x = factor(During.triage.were.you.handled.courteously.),
                       y = prop.table(stat(count)),
                       fill= factor(During.triage.were.you.handled.courteously.),
                       label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  scale_y_continuous(labels = scales::percent)+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  labs(x = "During triage were you handled courteously",y = "percentage proportion",title = "Whether customer was handled courteously ")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"),)+
  scale_fill_brewer(palette = "Dark2")+
  scale_x_discrete(labels = c("Did not respond","No","Yes"))

```

## Did the nurse explain the procedure above before performing it? 
```{r}
ggplot(data = data,aes(x=factor(Did.the.nurse.explain.the.procedure.above.before.performing.it.),
                       y=prop.table(stat(count)),
                         fill=factor(Did.the.nurse.explain.the.procedure.above.before.performing.it.),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Set2")+
  theme_light()+
  labs(x="Did the nurse explain the procedure above before performing it?",y="Percentage proportion",title = "Whether the Nurse explained procedure \n before performing it ")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","No","Yes"))
```


### Were the Health information officers courteous?
```{r}
ggplot(data = data,aes(x=factor(Were.the.Health.information.officers.courteous.),
                       y=prop.table(stat(count)),
                         fill=factor(Were.the.Health.information.officers.courteous.),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Set3")+
  theme_light()+
  labs(x="Were the Health information officers courteous?",y="Percentage proportion",title = "Whether the Health information officers courteous")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","No","Yes"))
```


## ***How do you rate the length of the following services?**
### Payment
```{r}
ggplot(data = data,aes(x=factor(Payment),
                       y=prop.table(stat(count)),
                         fill=factor(Payment),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Dark2")+
  theme_light()+
  labs(x="Customer rating of the length of paymet",y="Percentage proportion",title = "Rating of the length of paymet")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```


### Health information
```{r}
ggplot(data = data,aes(x=factor(Health.information),
                       y=prop.table(stat(count)),
                         fill=factor(Health.information),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Paired")+
  theme_light()+
  labs(x="Customer rating of Health information",y="Percentage proportion",title = "Rating of Health information")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```

### Triage
```{r}
ggplot(data = data,aes(x=factor(Triage),
                       y=prop.table(stat(count)),
                         fill=factor(Triage),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Dark2")+
  theme_light()+
  labs(x="Customer rating of Triage",y="Percentage proportion",title = "Rating of Triage")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```
# Doctor's review

```{r}
ggplot(data = data,aes(x=factor(Doctor.s.review),
                       y=prop.table(stat(count)),
                         fill=factor(Doctor.s.review),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_brewer(palette = "Accent")+
  theme_light()+
  labs(x="Customer rating of Doctor's review",y="Percentage proportion",title = "Rating of Doctor's review")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```


```{r}
ggplot(data = data,aes(x=factor(Appointment.booking),
                       y=prop.table(stat(count)),
                         fill=factor(Appointment.booking),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_viridis_d()+
  theme_light()+
  labs(x="Customer rating of Appointment booking",y="Percentage proportion",title = "Rating of Appointment booking")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))+
  scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```

## What.did.you.like.about.our.services
## Are there areas you would want us to improve on?


In future, would you seek health care services in this hospital?

```{r}
ggplot(data = data,aes(x=factor(In.future..would.you.seek.health.care.services.in.this.hospital.),
                       y=prop.table(stat(count)),
                         fill=factor(In.future..would.you.seek.health.care.services.in.this.hospital.),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_viridis_d(option = "C",end = .9)+
  theme_light()+
  labs(x="Customer rating of Appointment booking",y="Percentage proportion",title = "Rating of Appointment booking")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
  #scale_x_discrete(labels = c("Did not respond","Expected","Too Long"))
```


## Would you refer a friend/relative to Kenyatta National Hospital?

```{r}
ggplot(data = data,aes(x=factor(Would.you.refer.a.friend.relative.to.Kenyatta.National.Hospital.),
                       y=prop.table(stat(count)),
                         fill=factor(Would.you.refer.a.friend.relative.to.Kenyatta.National.Hospital.),
                         label=scales::percent(prop.table(stat(count)))))+
  geom_bar(position = "dodge")+
  geom_text(stat = 'count',
            position = position_dodge(.9),
            vjust= -0.5,
            size= 3)+
  scale_y_continuous(labels = scales::percent)+
   scale_fill_viridis_d(option = "B",end = .9)+
  theme_light()+
  labs(x="Customer rating of Appointment booking",y="Percentage proportion",title = "Rating of Appointment booking")+
  theme(legend.position = "none",plot.title = element_text(face = "bold"))
```

